---
title: "new drug list"
author: "Zongyan Wang"
date: "Monday, November 30, 2015"
output: pdf_document
---
# The .Rmd document returns the new drug proved by FDA for specified year
```{r}
if (!require("XML")) {
  install.packages("XML")
  library("XML") # this produces error if loading package fails
  }
```
## Functions used for this approach
### find the categories
```{r}
#' function findTheCategories
#'
#' The Function returns a categories list containing the web lines, categories 
#' and categories' line numbers
#'
#' Attention: the encode is currently set to UTF-8 for year 2013
#' @param year: the year of interest
#' @return a list
findTheCategories <- function(year){
  URL <- paste0("http://www.centerwatch.com/drug-information/fda-approved-drugs/year/", year)
  lines = readLines(URL, encoding = "UTF-8")
  categories.lines <- grep(pattern = "<h3>.*</h3>", x = lines, value = T)
  categories <- gsub(pattern = "<h3>(.*)</h3>", replacement = "\\1", x = categories.lines)
  ## Remove the whitespace in the strings
  categories <- gsub(pattern = " ", replacement = "", x = categories)
  ## All the categories
  categories
  categories.lineNum <- grep(pattern = "<h3>.*</h3>", x = lines)
  categories.lineNum[length(categories.lineNum) + 1] <- 
    grep(pattern = "<div id=\"BottomAdZone\">", x = lines) - 1
  return(list(lines = lines, categories = categories, categories.lineNum = categories.lineNum))
  }
```

### match the medicine name for each categories
The medicine is named as (Category_)medicineName_industryName
```{r}
#' function medicineFunction
#'
#' The Function returns a medicine list containing the categories, medicine and industry
#' The medicine is named as (Category_)medicineName_industryName
#'
#' 
#' @param categories.list: the categories.list returned from findTheCategories
#' @param category.name: TRUE if medicine name has the form Category_medicineName_industryName
#'                       FALSE if the form medicineName_industryName
#' @return a list

medicineFunction <- function(categories.list, category.name = FALSE){
  lines <- categories.list$lines
  categories <- categories.list$categories
  categories.lineNum <- categories.list$categories.lineNum
  medicine.list <- vector(mode="list", length=length(categories))
  names(medicine.list) <- categories
  for(i in 2: length(categories.lineNum)){
    key <- categories[i-1]
    categoryBlock <- lines[categories.lineNum[i-1]:categories.lineNum[i]]
    # find all the medicine in one particular block
    medicine.Line <- grep(pattern = "id=", x = categoryBlock, value = T)
    medicine.Line
    medicine <- gsub(pattern = "<p><strong><a id(.*)href(.*)>(.+)</a></strong>; (.*);", 
                     replacement  = "\\3_\\4", x = medicine.Line)
    # Remove the whitespace
    medicine <- gsub(pattern = "(\\s+)(\\w+.*)", replacement = "\\2", x = medicine)
    # Change the name as Category_medicineName_industryName
    if(category.name = T){
      medicine <- paste0(categories[i-1], "_", medicine)
    }   
    medicine.list[[key]] <- medicine
    }
  # Divide the lines into 28 blocks, each block is for one particular category
  return(medicine.list)
  }

```
## Use the functions to find the data interested
### Let find the medicine proved by FDA in 2013 first
```{r}
categories.list2013 <-findTheCategories(2013)
medicine.list2013 <- medicineFunction(categories.list2013)
medicine.list2013
```

## medicine proved by FDA in 2012
```{r}
categories.list2012 <-findTheCategories(2012)
medicine.list2012 <- medicineFunction(categories.list2012)
medicine.list2012
```

## medicine proved by FDA in 2011
```{r}
categories.list2011 <-findTheCategories(2011)
medicine.list2011 <- medicineFunction(categories.list2011)
medicine.list2011
```

# how to split the medicine in the list
medicine.list contains all the medicine proved by FDA in the year
You can get split the medicine name with the method strsplit()
```{r}
medicine.split.example <- strsplit(medicine.list2013[[1]], split = "_")

```

# What about a data frame?
## build a function
```{r}
#' function convertDataFrame
#'
#' The Function convert the medicine.list to a data.frame. CSV file output is an option
#'
#' 
#' @param medicine.list
#' @param output.csv: optional, boolean, true if a .csv is required
#' @param year: optional, added to the name of .csv output
#' @return a data.frame
convertDataFrame <- function(medicine.list, output.csv = FALSE, year = ""){
  nCol <- length(strsplit(medicine.list[[1]], split = "_")[[1]])
  medicine.dataframe <- data.frame()
  for(i in 1: length(medicine.list)){
    categories <- names(medicine.list[i])
    split <- strsplit(medicine.list[[i]], split = "_")
    name <- c()
    company <- c()
    categories <- rep(x = categories, times = length(split))
    for(j in 1:length(split)){
      if(nCol == 3){
        name <- c(name, split[[j]][2])
        company <- c(company, split[[j]][3])
      }else{
        name <- c(name, split[[j]][1])
        company <- c(company, split[[j]][2])
      }
    }
    df <- data.frame(category = categories, name = name, company = company)
    medicine.dataframe <- rbind(medicine.dataframe, df) 
  }
  if(output.csv == T){ 
    fileName = paste0("medicine_list_", year, ".csv")
    write.csv(medicine.dataframe, file = fileName, row.names = F)
    print(paste0(fileName, " has saved successfully into the current enviroment folder."))
  }
  return(medicine.dataframe) 
}



```
## Convert 2011 to 2013 file with .csv output
```{r}
medicine.dataframe2013 <- convertDataFrame(medicine.list2013, output.csv = T, year = 2013)
medicine.dataframe2012 <- convertDataFrame(medicine.list2012, output.csv = T, year = 2012)
medicine.dataframe2011 <- convertDataFrame(medicine.list2011, output.csv = T, year = 2011)

```