---
title: "StateByState"
author: "Zongyan Wang"
date: "Saturday, December 12, 2015"
output: pdf_document
---
# This document gives an overall analyst to the b/g ratio over States
# Load packages
```{r}
require(data.table)
require(agricolae)
require(plyr)
require(dplyr)
require(ggplot2)
require("XML")
require(RCurl)
```

# Load data
```{r}
partD_npi <- read.csv("F:/Academic/Stat 992/group project/prescription_fraud/analysis.py/NPI_bg.csv", header = T)
names(partD_npi)
npi_num <- partD_npi %>% group_by(NPPES_PROVIDER_STATE) %>%
  dplyr::summarize(length(NPI))
names(npi_num) <- c("State", "NPI_num")
```

# Overview of the data
## Get the population over states
```{r}
URL <- "http://simple.wikipedia.org/wiki/List_of_U.S._states_by_population"
Lines <- readLines(URL, encoding = "UTF-8")
states.lines <- grep(pattern = "<td align=\"left\"><span class=\"flagicon\"><img alt=\"\" src=", Lines, value = T)[1:50]
states.lineNum <- grep(pattern = "<td align=\"left\"><span class=\"flagicon\"><img alt=\"\" src=", Lines)[1:50]
pop.lineNum <- states.lineNum + 1
pop.lines <- Lines[pop.lineNum]
pop <- gsub(pattern = "(.+)>(.+)</td>", replace = "\\2", pop.lines)
states <- gsub(pattern = "(.*)title=(.+)</a></td>", replace = "\\2", states.lines)
states <- sub(pattern = "(.+)>(.+)", replace = "\\2", states)
states.pop <- data.frame(States = states, pop = pop)
```
## merge table with npi_num
```{r}
## change the data's States from capital Abbreviation to lower case full name
# get the abbreviation and full name online
URL <- "http://state.1keydata.com/state-abbreviations.php"
tables = readHTMLTable(URL, stringsAsFactors = FALSE)
list <- tables[[2]]
list <- data.frame(full = c(list$V1, list$V3), abb = c(list$V2, list$V4))
state <- list[-27, ][-1, ]
row.names(state) <- 1 : length(state[,1])
states.pop <- merge(state, states.pop, by.x = "full", by.y = "States")
npi_num <- merge(npi_num, states.pop, by.x = "State", by.y = "abb")
## convert pop from string with "," to integer
npi_num$pop <- lapply(npi_num[,"pop"], FUN = function(x) {gsub(pattern = ",", replace = "", x)})
npi_num$pop <- as.integer(npi_num$pop)
```
## NPI number over States
```{r}
## Total NPI number
length(partD_npi[,1])

# npi number over states
npi_num1 <- npi_num %>% 
  dplyr::mutate(State = reorder(x = State, X = NPI_num, FUN = min)) %>%
  arrange(., desc(NPI_num))
amount_over_states <- ggplot(npi_num1, aes(x = State, y = NPI_num)) +
  geom_point(aes(color = State)) +
  geom_text(aes(x = State, y = NPI_num, label = State, color = State), size = 3) +
  ggtitle("Amount of physicians over States")
ggsave(filename = "physician_over_states.png", plot = amount_over_states, dpi = 300, width = 8, height = 6)
```
## physician per 100 citizens
```{r}
npiPerC <- npi_num %>% mutate(npi_per_100 = 100 * NPI_num/pop)
## plot 
npiPerC <- npiPerC %>% 
  dplyr::mutate(State = reorder(x = State, X = npi_per_100, FUN = min)) %>%
  arrange(., desc(npi_per_100))
amount_per100_states <- ggplot(npiPerC, aes(x = State, y = npi_per_100)) +
  geom_point(aes(color = State)) +
  geom_text(aes(x = State, y = npi_per_100, label = State, color = State), size = 3) +
  ggtitle("physicians per 100 citizens over States")
amount_per100_states
ggsave(filename = "physician_per100_over_states.png", plot = amount_per100_states, dpi = 300, width = 8, height = 6)
```
## heatmap npi_num
```{r}
## drop the unnecessary areas
dropArea <- function(x){
  x <- x[which(x$NPPES_PROVIDER_STATE %in% state$abb),]
  row.names(x) <- 1 : length(x[,1])
  return(x)
}

## Make every alphabet to lower case
low <- function(x, state = state){
  index <- grep(pattern = as.character(x$State), state$abb)
  x$region <- state$full[index]
  x$region <- tolower(x$region)
  return(x)
}

Low <- function(data, state = state){
  y <- data %>% ddply(~State, function(x){low(x, state)})
  return(y)
}

# Get Average Latitude and Longitude for US States
location <- read.csv("state_latlon.csv")
names(location)[1] <- c("State")

loc <- function(x, location = location){
  x <- merge(x, location, by = "State")
  return(x)
}



## Plot USA map
heatmap1 <- function(x){
  states <- map_data("state")
  map.df <- merge(states,x, by="region", all.x=T)
  map.df <- map.df[order(map.df$order),]
  myPlot <- ggplot(map.df, aes(x=long,y=lat,group=group))+
    geom_polygon(aes(fill= NPI_num))+
    geom_path()+ 
    scale_fill_gradientn(colours=rev(heat.colors(20)),na.value="grey90")+
    geom_text(aes(x=longitude, y=latitude, label=State), 
              size=3) +
    ggtitle("HeatMap: Amount of physicians over States")+
    coord_map()
  myPlot
  return(myPlot)
}


## Draw npi_num
y1 <- npi_num
y1 <- Low(y1, state = state)
y1 <- loc(y1, location)
heatmap_npi_num <- heatmap1(y1)
heatmap_npi_num
ggsave(filename = "heatmap_npi_num.png", heatmap_npi_num, dpi = 300, width = 8, height = 6)
```
## heatmap npiPerC
```{r}
heatmap2 <- function(x){
  states <- map_data("state")
  map.df <- merge(states,x, by="region", all.x=T)
  map.df <- map.df[order(map.df$order),]
  myPlot <- ggplot(map.df, aes(x=long,y=lat,group=group))+
    geom_polygon(aes(fill= npi_per_100))+
    geom_path()+ 
    scale_fill_gradientn(colours=rev(heat.colors(20)),na.value="grey90")+
    geom_text(aes(x=longitude, y=latitude, label=State), 
              size=3) +
    ggtitle("HeatMap: physicians per 100 citizen over States")+
    coord_map()
  myPlot
  return(myPlot)
}
y2 <- npiPerC
y2 <- Low(y2, state = state)
y2 <- loc(y2, location)
heatmap_npiPerC <- heatmap2(y2)
heatmap_npiPerC
ggsave(filename = "heatmap_npiPerC.png", heatmap_npiPerC, dpi = 300, width = 8, height = 6)
```


# ANOVA without counting claim
```{r}
data <- cbind(partD_npi,trt=factor(partD_npi$NPPES_PROVIDER_STATE,labels=1:length(unique(partD_npi$NPPES_PROVIDER_STATE))))
model <- aov(b.g ~ trt, data = data)
summary(model)
```
The model shows significant result to States
## Doing LSD and HSD test
```{r}
lsd.out <- LSD.test(model, "trt", p.adj = "bonferroni")
hsd.out <- HSD.test(model,"trt", group = T)

#bar.group(lsd.out$groups,ylim=c(0,45),density=4,border="blue")
#bar.group(hsd.out$groups,ylim=c(0,45),density=4,border="blue")

#lsd.out$groups
#hsd.out$groups
```


## match the group number with States with the data we use
```{r}
id.group <- data %>% 
  dplyr::select(NPPES_PROVIDER_STATE, trt) %>%
  unique() %>%
  arrange(trt)
groups <- as.data.frame(hsd.out$groups)
groups$trt <- as.integer(groups$trt)  
id.group$trt <- as.integer(id.group$trt)
result1 <- plyr::join(groups, id.group)
result1
## print the result
result <- result1 %>% mutate(NPPES_PROVIDER_STATE = 
                              reorder(x = NPPES_PROVIDER_STATE, X = means, min)) 
ratio_without_claim <- ggplot(result, 
                              aes(x = NPPES_PROVIDER_STATE, y = means)) +
  geom_point(aes(color = M)) +
  geom_text(aes(x = NPPES_PROVIDER_STATE, y = means, 
                label = NPPES_PROVIDER_STATE), size = 3) +
  ggtitle("BPR without claim over States") +
  labs(x = "State", y = "means of BPR")
ratio_without_claim
ggsave(filename = "ratio_without_claim.png", ratio_without_claim, width = 8, height = 6, dpi = 300)

```

# ANOVA with counting claim
```{r}
data <- cbind(partD_npi,trt=factor(partD_npi$NPPES_PROVIDER_STATE,labels=1:length(unique(partD_npi$NPPES_PROVIDER_STATE))))
model <- aov(b.g.with.claim ~ trt, data = data)
summary(model)
```
The model shows significant result to States
## Doing LSD and HSD test
```{r}
lsd.out <- LSD.test(model, "trt", p.adj = "bonferroni")
hsd.out <- HSD.test(model,"trt", group = T)

#bar.group(lsd.out$groups,ylim=c(0,45),density=4,border="blue")
#bar.group(hsd.out$groups,ylim=c(0,45),density=4,border="blue")

#lsd.out$groups
#hsd.out$groups
```


## match the group number with States with the data we use
```{r}
id.group <- data %>% 
  dplyr::select(NPPES_PROVIDER_STATE, trt) %>%
  unique() %>%
  arrange(trt)
groups <- as.data.frame(hsd.out$groups)
groups$trt <- as.integer(groups$trt)  
id.group$trt <- as.integer(id.group$trt)
result2 <- plyr::join(groups, id.group)
result2
## print the result
result <- result2 %>% mutate(NPPES_PROVIDER_STATE = 
                              reorder(x = NPPES_PROVIDER_STATE, X = means, min)) 
ratio_with_claim <- ggplot(result, aes(x = NPPES_PROVIDER_STATE, y = means)) +
  geom_point(aes(color = M)) +
  geom_text(aes(x = NPPES_PROVIDER_STATE, y = means, 
                label = NPPES_PROVIDER_STATE), size = 3) +
  ggtitle("BPR over States") +
  labs(x = "State", y = "means of BPR")
ratio_with_claim
ggsave(filename = "ratio_with_claim.png", ratio_with_claim, width = 8, height = 6, dpi = 300)
```